### 2018-08-28 Sections/protocols_for_the_quantum_internet.tex
Telescope arrays

For the direct imaging of an object, diffraction limits the resolution of the image. When we consider two neighbouring points on the object separated by a small angle, the minimum angular separation resolvable is 
\begin{align}
	\theta_\mathrm{min} = 1.22 \frac{\lambda}{D},
\end{align}
known as the Rayleigh criterion\index{Rayleigh criterion}, $D$ being the diameter of the aperture\index{Aperture}.

@@

Thinking futuristically, in a future large-scale quantum internet, whereby Bell pairs are a readily available resource across the globe, quantum-enabled telescopy needn't be limited to pairs of telescopes, but could expand to become large-scale telescope arrays\index{Telescope arrays} comprising numerous telescopes, all sharing pairwise entanglement.

>>>>

For the direct imaging of an object, diffraction limits the resolution of the image. When we consider two neighbouring points on the object separated by a small angle, the minimum angular separation resolvable is,
\begin{align}
	\theta_\mathrm{min} = 1.22 \frac{\lambda}{D},
\end{align}
known as the Rayleigh criterion\index{Rayleigh criterion}, $D$ being the diameter of the aperture\index{Aperture}.

@@

Thinking futuristically, in a future large-scale quantum internet, whereby Bell pairs are a readily available resource across the globe, quantum-enabled telescopy needn't be limited to pairs of telescopes, but could expand to become large-scale telescope arrays\index{Telescope arrays} comprising numerous telescopes, all sharing pairwise entanglement, distributed via the quantum internet (see Fig.~\ref{fig:telescope_array}).

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{telescope_array}
	\caption{An array of quantum-enabled telescopes, paired with one another via Bell-pairs, distributed over a quantum network.}\label{fig:telescope_array}\index{Telescope arrays}
\end{figure}
